Gravitaitonal Wave Event Progenitor Synthesis

### 2022-05-26 src/tex/ms.tex
adding in new refs and praying the build works so I dont have to download the data locally

\noindent A small KL divergence means the reprojected \texttt{COSMIC} posterior is similar to the original posterior in the
observable space, and is thus a viable channel for that specific event. Otherwise, it either means \texttt{COSMIC}
can only explain part of the posterior or cannot explain the event at all. This is completely expected behavior since
\texttt{COSMIC}, and isolated binary evolution more generally, carries its own assumptions and is expected to
fail in reproducing a subset of the event in GWTC3. One example of this are GW events with at least one component
with mass above the pair instability supernova mass limit \kb{cite Farmer, and others}.
The reprojection could also be subject to stochasticity in the evolution of each binary
To account for this, we reproject the posterior multiple times with different random seeds and
check whether the KL divergence varies significantly. A varying KL divergence means a particular GW event is subject
to randomness in the evolution of the progenitor, and extra caution should be used when interpreting the result.

@@

We apply the method described in section \ref{sec:method} to the first GW event GW150914.
The parameters involved in the analysis and the range we allow for the inference are tabulated in table \ref{tab:parameters}.
The spin of BHs formed in isolated binaries depends strongly on the angular
momentum transport in massive stars which is still highly uncertain \kb{(see however Bavera+, fuller+)},
therefore we only consider the two component masses in the observable space in the both the
root-finding stage and the MCMC stage. For progenitor parameters, we characterize each guess with
five parameters: the two component masses $M_{\rm 1,ZAMS}$ and $M_{\rm 2,ZAMS}$, the orbital period $t_{\rm orb}$,
the eccentricity $e$, the metallicity $Z$ at ZAMS. Note that the progenitor formation redshift is not
obtained through the root-finding process because the formation redshift does not intrinsically affect
the evolution of the binary. Instead, we compute the time it takes for the binary to evolve from
formation to the merger and add this time back to the lookback time when a GW event is observed and limit the total
time to merger to be less than $13.7\,\rm{Gyr}$.
Using the total lookback time, we can compute the redshift of the binary at ZAMS formation following the
Planck 2018 cosmological model \citep{Planck2018}.
The main benefit of post-processing the redshift in this way is that we do not rely on a particular assumption
of star formation rate (SFR) distribution when we solve for the posterior distribution in redshift.
This means we can put the prior on formation redshift (or in general, metallicity-redshfit distribution) in
by reweighting the posterior distribution according to a particular SFR model,
and therefore do not have to rerun the inference everytime we change the SFR model. This is especially helpful
since SFR models are still highly uncertain but strongly impact the local merger rates of BBHs \citep{Broekgaarden2021}.
For hyperparameters, we choose parameters that affect
binary evolution in \texttt{COSMIC} mostly significantly for massive stars, including the common envelope
efficiency $\alpha$, the fraction of mass accreted onto the accretor during stable mass transfer $f_{\rm acc}$,
the critical mass ratio which determines whether Roche-overflow mass transfer
proceeds stably or produces a common envelope when the donor star is on the Hertzsprung gap
$q_{\rm crit,3}$, and the root-mean-square of the Maxwellian distribution
employed for CO natal kicks, $\sigma$.

@@

Events with more extreme mass ratios are hard to produce with \texttt{COSMIC},
and therefore less likely to be accurately recovered by our method. This could
be due to our method assuming a single value for $f_{\rm acc}$ and $\alpha$ as
discussed in Section~\ref{sec:result}.

>>>>

\noindent A small KL divergence means the reprojected \texttt{COSMIC} posterior is similar to the original posterior in the
observable space, and is thus a viable channel for that specific event. Otherwise, it either means \texttt{COSMIC}
can only explain part of the posterior or cannot explain the event at all. This is completely expected behavior since
\texttt{COSMIC}, and isolated binary evolution more generally, carries its own assumptions and is expected to
fail in reproducing a subset of the event in GWTC3. One example of this are GW events with at least one component
with mass above the pair instability supernova mass limit \citep{Woosley2017, Farmer2020}.
The reprojection could also be subject to stochasticity in the evolution of each binary
To account for this, we reproject the posterior multiple times with different random seeds and
check whether the KL divergence varies significantly. A varying KL divergence means a particular GW event is subject
to randomness in the evolution of the progenitor, and extra caution should be used when interpreting the result.

@@

We apply the method described in section \ref{sec:method} to the first GW event GW150914.
The parameters involved in the analysis and the range we allow for the inference are tabulated in table \ref{tab:parameters}.
The spin of BHs formed in isolated binaries depends strongly on the angular
momentum transport in massive stars which is still highly uncertain (see however \citet{Fuller2019, Bavera2020}),
therefore we only consider the two component masses in the observable space in the both the
root-finding stage and the MCMC stage. For progenitor parameters, we characterize each guess with
five parameters: the two component masses $M_{\rm 1,ZAMS}$ and $M_{\rm 2,ZAMS}$, the orbital period $t_{\rm orb}$,
the eccentricity $e$, the metallicity $Z$ at ZAMS. Note that the progenitor formation redshift is not
obtained through the root-finding process because the formation redshift does not intrinsically affect
the evolution of the binary. Instead, we compute the time it takes for the binary to evolve from
formation to the merger and add this time back to the lookback time when a GW event is observed and limit the total
time to merger to be less than $13.7\,\rm{Gyr}$.
Using the total lookback time, we can compute the redshift of the binary at ZAMS formation following the
Planck 2018 cosmological model \citep{Planck2018}.
The main benefit of post-processing the redshift in this way is that we do not rely on a particular assumption
of star formation rate (SFR) distribution when we solve for the posterior distribution in redshift.
This means we can put the prior on formation redshift (or in general, metallicity-redshfit distribution) in
by reweighting the posterior distribution according to a particular SFR model,
and therefore do not have to rerun the inference everytime we change the SFR model. This is especially helpful
since SFR models are still highly uncertain but strongly impact the local merger rates of BBHs \citep{Broekgaarden2021}.
For hyperparameters, we choose parameters that affect
binary evolution in \texttt{COSMIC} mostly significantly for massive stars, including the common envelope
efficiency $\alpha$, the fraction of mass accreted onto the accretor during stable mass transfer $f_{\rm acc}$,
the critical mass ratio which determines whether Roche-overflow mass transfer
proceeds stably or produces a common envelope when the donor star is on the Hertzsprung gap
$q_{\rm crit,3}$, and the root-mean-square of the Maxwellian distribution
employed for CO natal kicks, $\sigma$.

@@

Events with more extreme mass ratios are hard to produce with \texttt{COSMIC},
and therefore less likely to be accurately recovered by our method \citep[e.g.][]{Zevin2020}. This could
be due to our method assuming a single value for $f_{\rm acc}$ and $\alpha$ as
discussed in Section~\ref{sec:result}.
